---
title: "engines"
author: "Matthias Spichiger"
date: "2023-10-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## glue custom knitr language engines

Glue provides a few [custom language engines](https://bookdown.org/yihui/rmarkdown-cookbook/custom-engine.html#custom-engine) for knitr, which allows you to use glue directly in knitr chunks.

Use `Ctrl + Alt + I` to insert a new code chunk.


### `glue` engine

The first engine is the `glue` engine, which evaluates the contents as a glue template.
```{glue}
1 + 1 = {1 + 1}
```

Maybe the most useful use of the `glue`engine is to set the knitr option
`results = 'asis'` and output markdown or HTML directly into the document.
```{glue, results = 'asis', echo = FALSE}
#### mtcars has **{nrow(mtcars)} rows** and _{ncol(mtcars)} columns_
```


If you want to pass additional arguments into the `glue`call, simply include them as chunk options.
```{glue, .open = "<<", .close = ">>", results = 'asis', echo = FALSE}
The **median waiting time** between eruptions is <<median(faithful$waiting)>>.
```


### `glue_sql`engine

The second engine is `glue_sql`, which will use `glue::glue_sql()` to generate a SQL query and then run the query using the `sql_engine`.

First we create a new connection to an in-memory SQLite database,
and write a new table to it.

```{r}
con <- DBI::dbConnect(drv = RSQLite::SQLite(), ":memory:")
mtcars$model <- rownames(mtcars)
DBI::dbWriteTable(conn = con, name = "mtcars", value = mtcars)
```

Next define some variables we can use with `glue` to interpolate

```{r}
var <- "mpg"
tbl <- "mtcars"
num <- 150
```

Then we can use `glue_sql`to construct and run a query using those variables in that database.
*Note* you need to provide the connection object as the `connection` chunk option.

In this example there are two types of quotes.
The first are bare back ticks. These are passed directly to the SQL engine.
The second are back ticks inside of braces, which are interpreted by `glue` to do the proper quoting for the given SQL engine.
In this example, we use the `sqlite`engine, which uses back ticks for quoting, but you would use the same back ticks inside the brace syntax for `postgreSQL` and `glue::glue_sql()` would automatically use double quotes for quoting instead.
```{glue_sql, connection = con}
SELECT `model`, `hp`, {`var`}
FROM {`tbl`}
WHERE {`tbl`}.hp > {num}
```

